---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr}
  %\usepackage[utf8]{inputenc}
---

Motivation 
==================

#### *"Write software as if you were writing for someone else - for in six months you will be someone else!" - Brian Kernighan and P. J. Plauger*

- Reproducible 
- Transparent
- Flexible/Robust
- Accessible

***

Useful resources:
====================

- Creating R packages in R studio - [Jeff Allen's Youtube][1]
- Analyses as Packages - [Robert M Flight's post on R-bloggers][2]
- Literate statistical programming with knitr - [Roger Peng's Youtube][3]
- Online book - [R packages by Hadley Wickham][4] 
- General guidence - [Writing R extensions][5]  

***

Required Packages/Sofwares Preparation 
========================================

- Devtool
- Roxygen2 
- Knitr 

***

Workflow
===========================
#### Step 1 : Start a project in RStudio and set up a set of project options:        
    - Set default sweave engine - Knitr
    - Function documentation - Roxygen2

#### Step 2 : Write sripts 
      - getSquareSum.R
      - calPI.R

#### Step 3 : Build R packages with documentation 
  
    - To write a vignette, devtools::use_vignette("title")
    - Write the content of vignettes
    - Run devtools::build_vignettes()
  
    - R CMD check "package-name"
    - R CMD build "package-name"  
    - R CMD install "package-name"
***

Writing vignettes for a package
=============

##### Example: How to caculate PI 

###### Use square sum function! 
```{r}
library(FirstProj)
#You get the square sum of two input values
squareSum(2,4)
```


##### Use calPI(N) function with N trials 
```{r}
#You calculate the PI using Monte-Carlo simulation
result <- calPI(1000)
cat("Estimated Pi value is", result$PI, "\n")
```

##### The idea is illustrated in the following figure
You throw random numbers x, y in the square. Count the number of times it is in the circle. That will give you the area of circle. Or the estimated value of PI.  

```{r}
library("plotrix")
x = runif(100, -1, 1)
y = runif(100, -1, 1)
plot(x, y, asp = 1, xlim = c(-1, 1))
draw.circle(0, 0, 1, nv = 1000, border = "Red", col = NA, lty = 1, lwd = 1)
```

[1]: https://www.youtube.com/watch?v=9PyQlbAEujY
[2]: http://www.r-bloggers.com/analyses-as-packages/
[3]: https://www.youtube.com/watch?v=YcJb1HBc-1Q
[4]: http://r-pkgs.had.co.nz/
[5]: http://cran.r-project.org/doc/manuals/r-release/R-exts.html


